---
title: "Homework 2"
date: 2020-09-30
author: "Michelle Lee"
output: github_document
---

This is my solution to HW2.
```{r}
library(readxl)
library(tidyverse)
library(dplyr)
```
##read in data trash_wheel, sheet Mr. Trash Wheel
```{r}
trash_wheel= read_excel("~/Desktop/P8105_github/data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", 
    sheet = "Mr. Trash Wheel", na = "NA")
trash_wheel= janitor::clean_names(trash_wheel)
names(trash_wheel)
```
#round the number of sports balls to the nearest integer and converts the result to an integer variable (using as.integer)

```{r}
sb= round(trash_wheel[['sports_balls']])
trash_wheel = mutate(trash_wheel, sports_balls = as.integer(sb))

```
The median number of sports balls 
#read in precp. data 2017, 2018

```{r}

prec_2018= read_excel("~/Desktop/P8105_github/data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", 
    sheet = "2018 Precipitation", skip=1)
drop_na(prec_2018, Month)
prec_2018= janitor::clean_names(prec_2018)
#names(prec_2018)
prec_2018 = mutate(prec_2018, year = 2018)

prec_2017= read_excel("~/Desktop/P8105_github/data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", 
    sheet = "2017 Precipitation", skip=1)
drop_na(prec_2017, Month)
prec_2017= janitor::clean_names(prec_2017)
#names(prec_2017)
prec_2017 = mutate(prec_2017, year = 2017)

prec_17_18 = 
  left_join(prec_2017, prec_2018, by = "month")
prec_17_18 = mutate (prec_17_18, month = month.name[month])
prec_17_18
```
In total, it rained significantly more in year 2018. In 2017, October, there was no record of precipitation. The total precipation in 2018 was 70.33 inches. 

#problem 2
```{r}
nyc_transit_raw = read_csv("~/Desktop/P8105_github/data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv",
            )
nyc_transit_clean_names= janitor::clean_names(nyc_transit_raw)
names(nyc_transit_clean_names)
nyc_transit_clean_names

nyc_transit_selected= 
  select(nyc_transit_clean_names, line, station_name, station_latitude, station_longitude, route1:11, entry, vending, entrance_type, ada)
#nyc_transit_selected

nyc_transit_entry_logic = 
mutate (nyc_transit_selected, entry = recode(
  entry, 'YES' = '1', 'NO' = '2'))
nyc_transit_entry_logic 
dim(nyc_transit_entry_logic)
#1868   14
```

nyc_transit_selected contains important data to analyze line, station name/location, ada compliance, routes, and entry type. The final dimension of nyc_transit_entry_logic is 1868 X 14. These data are not tidy, and can be improved by pivoting the route options. 

```{r}
stations_dist=
distinct(nyc_transit_entry_logic, station_latitude, station_longitude,ada)
stations_dist
```
There are 472 distinct stations, identified by latitude and longitude of the station location.

```{r}
dplyr::filter(stations_dist, grepl ('TRUE', ada))
```
There are 91 distinct stations that are ada compliant.
```{r}
nyc_transit_vending =
distinct(nyc_transit_selected, station_latitude, station_longitude,vending, entry)
nyc_transit_vending
dplyr::filter(nyc_transit_vending, grepl ('NO', vending))
dplyr::filter(nyc_transit_vending, grepl ('YES', entry))
#112
```
There are 112 stations without vending that allow entrance, out of 472 unique stations, indicating a proportion of 23.72%.
